---
title: "Perception, Memory, and Coordination"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Alexandra Paxton} \\ \texttt{paxton.alexandra@gmail.com} \\ Institute of Cognitive and Brain Sciences \\ Berkeley Institute for Data Science \\ University of California, Berkeley
    \And {\large \bf Thomas J. H. Morgan} \\ \texttt{thomas.j.h.morgan@asu.edu} \\ School of Human Evolution and Social Change \\ Arizona State University
    \AND {\large \bf Jordan W. Suchow} \\ \texttt{suchow@berkeley.edu} \\ Social Science Matrix \\ University of California, Berkeley
    \And {\large \bf Thomas L. Griffiths} \\ \texttt{tom\_griffiths@berkeley.edu} \\ Department of Psychology \\ University of California, Berkeley}
    
abstract: 
    "With cognitive scientists' increasing interest in moving outside of the lab, recent advances in crowdsourcing platforms can help strike a balance between the tight experimental control of lab designs and the affordances of web-based experiments to reach beyond traditional undergraduate subject pools. By taking advantage of new tools, scientists interested in social cognition and behavior can create new designs and adapt traditional ones to deliver experiments at scale. Dallinger is one such tool, providing researchers with an open-source experiment platform that provides end-to-end automation of the experiment pipeline, from participant recruitment and consent to data de-identification and participant compensation. Here we demonstrate how Dallinger can be used to run complex experimental studies of interactive human social behavior, as a demonstration of its potential to study social cognition and behavior using designs drawn from across cognitive science."
    
keywords:
    "interpersonal interaction; human communication; crowdsourcing; Dallinger"
    
output: cogsci2016::cogsci_paper
  
---

```{r global_options, include=FALSE}

# clear our workspace
rm(list=ls())

# set global options
require("knitr")
opts_knit$set(root.dir = "../")
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/', echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r import-and-prep-data, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# read in the libraries and functions we'll need
source('./supplementary-code/required_packages-pmc.r')
source('./supplementary-code/libraries_and_functions-pmc.r')

# convert the most recent 'perception-memory-coordination.Rmd' to file 
most_recent_pmd = paste0("./supplementary-code/pmc-rmd_to_code-",
                    as.character(as.Date(file.info('perception-memory-coordination.Rmd')$mtime)))
rmd2rscript(infile = './perception-memory-coordination.Rmd',
            outname = most_recent_pmd)

# then source it
source(paste0(most_recent_pmd,'[rmd2r].R'))

# load in participant information
participant_counts = read.table('./data/participant_pairs.csv', sep = ',',
                              header=TRUE)
participant_time = read.table('./data/participant_duration.csv', sep = ',',
                              header=TRUE)
participant_bonuses = read.table('./data/participant_bonuses.csv', sep = ',',
                              header=TRUE)

```

# Introduction

# Method

All research activities were completed in compliance with oversight from Committee for the Protection of Human Subjects at the University of California, Berkeley.

## Participants

Participants (*n* = `r length(participant_counts$dyad)*2`) were individually recruited from Amazon Mechanical Turk to participate as dyads (*n* = `r length(participant_counts$dyad)`). Participants were paired with one another according to the order in which they began the experiment. All participants were over 18 years of age and fluent English speakers (self-reported), located within the U.S.

The experiment lasted an average of `r round(mean(participant_time$duration),2)` minutes (range: `r round(min(participant_time$duration),2)`---`r round(max(participant_time$duration),2)` minutes). In return for their participation, all participants were paid \$1.33 as base pay for finishing the experiment. Each participant also earned a bonus based of up to \$2 for the entire experiment based on mean accuracy over all trials (mean = \$`r round(mean(participant_bonuses$bonus-.33),2)`; range: \$`r round(min(participant_bonuses$bonus-.33),2)`---\$`r round(max(participant_bonuses$bonus-.33),2)`).

## Procedure

All data collection procedures occurred on Dallinger (http://github.com/dallinger/Dallinger), deployed on Amazon Mechanical Turk (http://mturk.com). Code for the experiment is available on GitHub: http://github.com/thomasmorgan/joint-estimation-game, and the resulting experiment data are available on the OSF repository for the project: https://osf.io/8fu7x/.

Each participant was individually recruited on Amazon Mechanical Turk to play a "Line Estimation Game" advertised as a way to "Test your memory skills!".

Participants were given no information about their partner other than the guess that their partner made.

## Analyses

# Results

# Discussion

# Conclusion

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r references}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent


<!-- # Formalities, Footnotes, and Floats -->

<!-- Use standard APA citation format. Citations within the text should -->
<!-- include the author's last name and year. If the authors' names are -->
<!-- included in the sentence, place only the year in parentheses, as in -->
<!-- [-@NewellSimon1972a], but otherwise place the entire reference in -->
<!-- parentheses with the authors and year separated by a comma -->
<!-- [@NewellSimon1972a]. List multiple references alphabetically and -->
<!-- separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a].  -->
<!-- Use the et. al. construction only after listing all the authors to a -->
<!-- publication in an earlier reference and for citations with four or -->
<!-- more authors. -->

<!-- For more information on citations in R Markdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).** -->

<!-- ## Footnotes -->

<!-- Indicate footnotes with a number\footnote{Sample of the first -->
<!-- footnote.} in the text. Place the footnotes in 9 point type at the -->
<!-- bottom of the page on which they appear. Precede the footnote with a -->
<!-- horizontal rule.\footnote{Sample of the second footnote.} -->

<!-- ## Figures -->

<!-- All artwork must be very dark for purposes of reproduction and should -->
<!-- not be hand drawn. Number figures sequentially, placing the figure -->
<!-- number and caption, in 10 point, after the figure with one line space -->
<!-- above the caption and one line space below it. If necessary, leave extra white space at -->
<!-- the bottom of the page to avoid splitting the figure and figure -->
<!-- caption. You may float figures to the top or bottom of a column, or -->
<!-- set wide figures across both columns. -->

<!-- ## Two-column images -->

<!-- You can read local images using png package for example and plot  -->
<!-- it like a regular plot using grid.raster from the grid package.  -->
<!-- With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.** -->

<!-- You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`. -->

<!-- ```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."} -->

<!-- ``` -->

<!-- ## One-column images -->

<!-- Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`. -->

<!-- ```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."} -->

<!-- ``` -->


<!-- ## R Plots -->

<!-- You can use R chunks directly to plot graphs. And you can use latex floats in the -->
<!-- fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)** -->

<!-- ```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" } -->
<!-- x <- 0:100 -->
<!-- y <- 2 * (x + rnorm(length(x), sd = 3) + 3) -->

<!-- ggplot2::ggplot(data = data.frame(x, y),  -->
<!--        aes(x = x, y = y)) +  -->
<!--   geom_point() +  -->
<!--   geom_smooth(method = "lm") -->
<!-- ``` -->


<!-- ## Tables -->

<!-- Number tables consecutively; place the table number and title (in -->
<!-- 10 point) above the table with one line space above the caption and -->
<!-- one line space below it, as in Table 1. You may float -->
<!-- tables to the top or bottom of a column, set wide tables across both -->
<!-- columns. -->

<!-- You can use the xtable function in the xtable package. -->

<!-- ```{r xtable, results="asis"} -->
<!-- n <- 100 -->
<!-- x <- rnorm(n) -->
<!-- y <- 2*x + rnorm(n) -->
<!-- out <- lm(y ~ x) -->

<!-- tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2),  -->
<!--                       caption = "This table prints across one column.") -->

<!-- print(tab1, type="latex", comment = F, table.placement = "H") -->
<!-- ``` -->
